A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-10-28 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
edited effects of failure on compromised groups

Show analytical results in comparison with simulation

@@

\subsection{Convergence pressures}

The model primarily converges to steady state due to factors such as
signature request frequency, node availability, and group creation/expiration. We discuss a few
steady state values of interest.

@@

\textit{Group Size} in all distributions group size appears to reduce the percentage
of lynchpinned signatures and compromised groups. Intuitively this makes since since 
as we increase the size of a group, we include more group owners who may not be malicious. 
comment on degree of change?

@@

\section{Conclusion and Future work}
This theoretical analysis highlighted possible behaviors of the Keep network beacon. we
validated the model using some simple analytical methods. However, once the beacon launches
we can use real data from the network to validate and adjust the model. At this point we can
then use the model to better investigate future behaviours and causes of behavior.

>>>>

Show analytical results in comparison with simulation?

\subsection{Compromised Groups}
We use the survival function of the hypergeometric distribution to determine
the likelihood of a group of n members being compromised. To do this we evaluate
the function at the max malicious threshold. (in the sim we have a separate compromised threshold)

\subsection{Node Attrition, Failures, and Inactivity}
We model Node attrition and failures as Binomial, and Inactivity as a function of 
the two.

Describe mathematically....

\subsection{Lynchpinned Signatures}

\subsection{Failed Signatures}

@@

\subsection{Convergence pressures}
The model primarily converges to steady state due to factors such as
signature request frequency, node availability, and group creation/expiration. We discuss a few
steady state values of interest.

@@

\textit{Group Size} in all distributions group size appears to reduce the percentage
of lynchpinned signatures but have no impact on compromised groups. Our defininition of compromised
groups is independent of node failure's and therefore the variation shown is likeley not related to
node failure.

comment on degree of change?

@@

\newpage
\section{Conclusion and Future work}[h!]
This theoretical analysis highlighted possible behaviors of the Keep network beacon. we
validated the model using some simple analytical methods. However, once the beacon launches
we can use real data from the network to validate and adjust the model. At this point we can
then use the model to better investigate future behaviours and causes of behavior.
